Tail Indices and Scale Parameters in Financial Time Series

### 2017-02-27 papers/FX/draft.tex
Looked again at the variation of K.
We need to do some estimation about the assumed model.

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation*}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x < 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation*}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\[
u(v) + b u(\delta v))
=
\E u(C) + b \E [u(C); C < \delta v]
\]
The right-hand-side of the above equation is a functional of the
distribution function of $X$ via eq.\eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v]
\]
$C < \delta v$ implies
\[
X < -q(r, \phi, \delta v) := \ln \left( {
  \delta v - (1 - \phi) e^r
  \over
  \phi
} \right)
\]
In the rest of this section we write $q$ for $q(r, \phi, \delta v)$
for convenience. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \1{x < -q} \over (K + x)^{\alpha + 1}} dx \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < -q} \over (K' + x)^{\beta + 1}} dx
  \label{eq:xxie1.0}
\end{eqnarray}

@@

%% with continuous and strictly increasing
%% distribution function $F(\cdot)$. Cheng and Peng (2001)
%% \cite{cheng2001confidence} showed asymptotic normal distribution of
%% the estimator $\alpha_n$:
%% \begin{proposition}\label{prop:Hill_asymp_dist}
%%   Suppose $X_1, ..., X_n$ are independent identically distributed and
%%   their distribution function $F(\cdot)$ satisfies, as $x \to \infty$,
%%   \[
%%   1 - F(x) = A x^{-\alpha} [1 + B x^{-\beta} + o(x^{-\beta})]
%%   \]
%%   where $A, \alpha, \beta > 0$ and $B \neq 0$. Then
%%   \[
%%   \sqrt k (1/\alpha_n - 1/\alpha) \overset{d}{\to}
%%   N(0, {1 \over \alpha^2})
%%   \]
%%   if and only if $k(n) \to \infty$ and $k(n) = o(n^{2\beta/(\alpha +
%%     2\beta)})$.
%% \end{proposition}
%% \begin{proof}
%%   This is proposition 1 of Cheng and Peng (2001)
%%   \cite{cheng2001confidence}. See also Embrechts et al (1997)
%%   \cite{Embrechts1997}.
%% \end{proof}

\section{Peaks over Threshold}
An alternative to the Hill estimator is the method of ``Peaks over
Threshold'' (cf. Embrechts et al (1997)
\cite{Embrechts1997}). Consider random variable $X$ whose distribution
satisfies 
\[
\P(X > x) = A (x + a)^{-\alpha}
\]
for all $x > M$ for some $M > 0$. Then it immediately follows
\begin{eqnarray*}
  \P(X > u + x)
  &=& A (u + a)^{-\alpha} \left(
  {x \over u + a} + 1
  \right)^{-\alpha} \\
  \P(X > u + x | X > u) &=& \left(
    {x \over u + a} + 1
    \right)^{-\alpha}
\end{eqnarray*}
The density function of the above conditional probability is
\[
f_u(x) = {
  \alpha \over x + u + a
} \left(
{x \over u + a} + 1
\right)^{-\alpha}
\]

Now suppose we have a sample $X_1, ..., X_N$ where $X_1, ..., X_n > u$
and $X_i - u = x_i > 0$, for $i=1,2,...,n$. Using the above
conditional density function, the log-likelihood function of the
parameters $\alpha$ and $a$ can be found:
\[
L(u, a) = -(1 + \alpha) \sum_{i=1}^n \ln(x_i + u + a) +
u \alpha \ln(u + a) + n \ln(\alpha)
\]
It follows
\begin{eqnarray*}
  \pd{L(\alpha, a)}{\alpha} &=& \sum_{i=1}^n \ln(x_i + u + a)
  + n \ln(u + a) + n/\alpha \\
  \pd{L(\alpha, a)}{a} &=&
  -(1 + \alpha) \sum_{i=1}^n {1 \over x_i + u + a}
  + {n \alpha \over u + a}
\end{eqnarray*}
Setting the two derivatives to 0 gives
\begin{eqnarray*}
  \left[
    {1 \over n} \sum_{i=1}^n \ln(x_i + u + a)
    - \ln(u + a)
    \right]^{-1} &=& \alpha\\
  \left[
    {1 \over n} \sum_{i=1}^n (y_i + 1)
    \right] \left[
    {1 \over n} \sum_{i=1}^n e^{-y_i}
    \right] &=& 1
\end{eqnarray*}
where
\begin{eqnarray*}
  y_i &=& \ln\left(
  {x_i \over u + a} + 1
  \right)
\end{eqnarray*}
Solving the last equation numerically and substituting the result into
the first one gives an estimate for $\alpha$ and $a$, call them $\hat
\alpha$ and $\hat a$. Once $\hat \alpha$ and $\hat a$ have been
obtained, an estimate of $A$, call it $\hat A$, can be obtained by
the method of minimum mean square error.
\begin{eqnarray*}
  \hat P(X > x) = {1 \over N} \sum_{i=1}^N \1{X_i > x}
  &=& \hat A (x + \hat a)^{-\hat \alpha} \\
  \ln[\hat P(X > x)] &=& \ln(\hat A) - \hat \alpha \ln(x + \hat a)
\end{eqnarray*}
for all $x > M$. Using the upper order statistics of the
sample $X_1, ..., X_N$, we have
\[
\ln\left({k-1 \over N}\right)
=
\ln(\hat A) - \hat \alpha \ln(X_{(k)} + \hat a)
\]
where $X_{(k)}$ denotes the $k$-th upper order statistic of the
sample. Thus, by fitting $\ln\left({k-1 \over N}\right)$ as a linear
function of $\ln(X_{(k)} + \hat a)$, one can find $\ln(\hat A)$ as the
intercept.

Before computing the estimates, one should certainly check whether the
model makes sense for a given data series. One way to do this is to
plot the {\it mean excess function}. For the tail function in the
above, it follows
\begin{eqnarray}
  e(u) &=& \E (X - u | X > u) \nonumber \\
  &=& -\int_0^\infty x  d\P(X > u + x | X > u) \nonumber \\
  &=& \int_0^\infty \left(
  {x \over u + a} + 1
  \right)^{-\alpha} dx \nonumber \\
  &=& {u + a \over \alpha - 1} \label{eq:MEF}
\end{eqnarray}
where we assume $\alpha > 1$ so that the conditional expectation is
finite. It is seen from this formula that mean excesses are linear in
the thresholds $u$ -- this may prompt discarding the farthest tail
part of the data when carrying out estimation.
%% The appearance of these data points are so rare that
%% including them in the statistics significantly increases the variance
%% of the estimate. This is analogous to the large variance of the Hill
%% estimator when the number of upper order statistics used in the
%% estimation is too small.
\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \includegraphics[width=0.45\textwidth]{ADM_MEF.pdf}
  \caption{\scriptsize The mean excess function of ADM. Thresholds are
    taken from upper order statistics.}
  \label{fig:ADM_MEF}
\end{wrapfigure}

For example, figure (\ref{fig:ADM_MEF}) shows the mean
excess function of the return series of the stock of {\it
  Archer-Daniels-Midland Co}, a company in the {\it Consumer Staples}
sector of S\&P 500 index.
One can see that the 8 largest observations of the sample are
inconsistent with the linear pattern with slope $1/(\alpha - 1)$.
%% So we would rather not include them in the maximum likelihood
%% estimation.

It is also possible to directly use equation \eqref{eq:MEF} as a means
of estimation. After picking out a portion of the mean excess function
that is consistent with \eqref{eq:MEF}, one may fit a linear function
to the empirical $\hat e(u)$ by minimizing the mean square error, and
obtain parameter estimates from the coefficients of the fitted line.
  %% \adjustbox{valign=t} {
  %%   \begin{minipage}[t]{0.45\textwidth}
  %%   \end{minipage}
  %% }\hfill
  %% \adjustbox{valign=t} {
  %%   \begin{minipage}[t]{0.5\textwidth}
  %%   \end{minipage}
  %% }
\section{Pickand's Estimator}
Pickands (1975) \cite{pickands1975statistical} proposed a different
approach to estimate the tail index than that of Hill. Assume
$\{x_i\}_{i=1}^n$ are samples from the distribution of $X$ and let $U(t)$
denote the quantile of $1 - 1/t$ of this distribution, i.e.
\[
P(X > U(t)) = {1 \over t}
\]
The key idea of Pickands' estimator is to observe
\[
\lim_{t \to \infty} {
  U(c(t) t) - U(t)
  \over
  U(t) - U(t/c(t))
} = 2^{1/\alpha}
\]
for any function $c(t)$ satisfying $c(t) \to 2$ as $t \to \infty$.
Pickands formulated the estimation problem in terms of the extreme
value index $\xi$, which is the reciprocal of the tail index $\alpha$
when the distribution of $X$ is regularly varying (cf. Embrechtsm,
Kl\"uppelberg and Mikosch \cite{Embrechts1997}).

@@

%% and show that, within a
%% comfortable confidence interval, one cannot reject the null hypothesis
%% that these return series have the same tail index.

\subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
Figure \ref{fig:Energy_Hill_upper} shows the Hill estimates of the
tail indices of 32 stocks in the {\it Energy} sector of S\&P 500
index; figure \ref{fig:Consumer_Staples_Hill_upper} shows the same of
the {\it Consumer Staples} sector.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 32 stocks'
    daily return series in the {\it Energy} sector of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=(\ln n)^2 = 49$ upper order statistics are used
    for computing $\alpha_n$. 
  }
  \label{fig:Energy_Hill_upper}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 30 stocks'
    daily return series in the {\it Consumer Staples} sector of
    Standard \& Poor 500 index.
  }
  \label{fig:Consumer_Staples_Hill_upper}
\end{figure}
For our purpose, we have excluded a few stocks, though:
\begin{figure}[htb!]
  \centering
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{WBA_price.pdf}
    \caption{{\it Walgreens Boots Alliance} prices}
    \label{fig:EBA_prices}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{WFM_price.pdf}
    \caption{{\it Whole Foods Market} prices}
    \label{fig:WFM_prices}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{EL_price.pdf}
    \caption{{\it Estee Lauder Cos.} prices}    
    \label{fig:EL_prices}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{CL_price.pdf}
    \caption{{\it Colgate-Palmolive} prices}    
    \label{fig:CL_prices}
  \end{subfigure}
  \caption{Plot of prices of {\it Consumer Staples} stocks
    excluded from Hill estimates}
\end{figure}

\begin{itemize}
\item {\it Walgreens Boots Alliance}:

  As shown in figure (\ref{fig:EBA_prices}),
  this stock was traded only in a small fraction of the bank
  days and it is hence no surprise that the price varied
  tremendously.
\item {\it Whole Foods Market}, {\it Estee Lauder Cos.} and {\it
  Colgate-Palmolive}

  As seen in figures (\ref{fig:WFM_prices}), (\ref{fig:EL_prices}) and
  (\ref{fig:CL_prices}),
  the prices of these stocks were reduced by half during the
  period under consideration. But the price changes are the
  result of emission of new shares rather than random fluctuations.
\end{itemize}

Figure \ref{fig:Energy_Hill_upper} and
\ref{fig:Consumer_Staples_Hill_upper}
are suggestive of the conclusion that excluding price
movements due to deterministic events, tail indices of stock return
series tend to have the same value, within a reasonable confidence
interval.

If we look instead at the scales, differences among the stock return
series are however rather large. Figure (\ref{fig:Energy_Hill_Scales})
and (\ref{fig:Consumer_Staples_Hill_Scales}) show the Hill estimates of
the scale parameters of the stocks in the S\&P 500 {\it Energy} and
{\it Consumer Staples} sectors, respectively.
\begin{figure}[htb!]
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{Energy_Hill_scales.pdf}
    \caption{{\it Energy} scale estimates}    
    \label{fig:Energy_Hill_Scales}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{Consumer_Staples_Hill_scales.pdf}
    \caption{{\it Consumer Staples} scale estimates}    
    \label{fig:Consumer_Staples_Hill_Scales}
  \end{subfigure}
  \caption{Black boxes are Hill estimates of the scale parameters of
    the stock return series, while red circles are the scale estimates
    of simulated iid. Student's $t$ series with a degree of freedom
    equal to the mean value of the estimated tail indices of the stock
    return series. The estimates of the Student's $t$ series are
    included for comparison with those of the return series.}
\end{figure}
Clearly the estimated scale parameters can differ by several orders of
magnitude.

Using the ``Peaks over Threshold'' method and the mean excess
function, we also obtain estimates for the tail index ($\alpha$), the
scale parameter ($A$) and the shift parameter ($a$) for stocks in the
{\it Energy} and the {\it Consumer Staples} sectors of the S\&P 500
index. The results are plotted in figure
\ref{fig:Energy_OLS_estimates} and
\ref{fig:Consumer_Staples_OLS_estimates},
respectively.
\begin{figure}[htb!]
  \includegraphics[width=\textwidth]{Energy_OLS_estimates.pdf}
  \caption{Tail parameter estimates of {\it Energy} stocks. The top
    plot shows the tail index estimates, the middle plot shows the
    10-based logarithm of the scale estimates and bottom plot shows
    the estimates of the shift parameter.
  }
  \label{fig:Energy_OLS_estimates}
\end{figure}

\begin{figure}[htb!]
  \includegraphics[width=\textwidth]{Consumer_Staples_OLS_estimates.pdf}
  \caption{Tail parameter estimates of {\it Consumer Staples}
    stocks. The top 
    plot shows the tail index estimates, the middle plot shows the
    10-based logarithm of the scale estimates and bottom plot shows
    the estimates of the shift parameter.
  }
  \label{fig:Consumer_Staples_OLS_estimates}
\end{figure}

@@

\subsubsection{The Information Technology sector of S\&P 500}
Compared with the sectors of energy and consumer staples, which enjoy
a relatively stable demand on their products, companies of information
technology are more subject to volatile demand and competition. As a
result, one can expect their stock prices to be more volatile, implying
lower tail indices and larger differences between the tail indices of
different companies. In this section we investigate how these companies
differ in terms of their tail indices and scale parameters.

Figure \ref{fig:Information_Technology_Hill} shows the Hill
estimates of 42 stocks in the {\it Information Technology} sector. Daily
closing prices of these stocks have been available since 2000-01-01 and
earlier.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Information_Technology_Hill.pdf}
  \caption{Hill estimates of the tail indices of 42 stocks' daily
    return series in the {\it Information Technology} sector of Standard
    \& Poor 500 index.
  }
  \label{fig:Information_Technology_Hill}
\end{figure}
It is seen in the figure that most of the estimates fall within the
interval spanned by the confidence bands. Thus, given the estimation
precision, these are consistent with the similarity conclusion of 
\S\ref{sec:GDA}.

@@

\subsection{Temporal changes of the parameters}

@@

\bibliographystyle{unsrt}
\bibliography{my_citations}
\end{document}

>>>>

\subsubsection[in case gamma > 1]{in case $\gamma > 1$}
In this section we consider power utility functions of
\eqref{eq:power_utility} with $\gamma > 1$. For convenience,
let $\xi = \gamma - 1$. In this case, we assume the following
distribution function $F(\cdot)$ of the equity return:
\begin{equation}
  \label{eq:X_distr}
  F(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x < 0 \\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0
  \end{array}
  \right.
\end{equation}
Assume $\alpha, \beta > 1$, $0 < p < 1$ and $K > 0$.
Equation
\eqref{eq:xxie0} can be re-arranged as
\[
u(v) + b u(\delta v))
=
\E u(C) + b \E [u(C); C < \delta v]
\]
The right-hand-side of the above equation is a functional of the
distribution function of $X$ via eq.\eqref{eq:xxie1}. For convenience
we denote it $\mathcal U(\cdot)$, i.e.
\[
\mathcal U F (\alpha, \beta, K, K', \phi)
= 
\E u(C) + b \E [u(C); C < \delta v]
\]
$C < \delta v$ implies
\[
X < -q(r, \phi, \delta v) := \ln \left( {
  \delta v - (1 - \phi) e^r
  \over
  \phi
} \right)
\]
In the rest of this section we write $q$ for $q(r, \phi, \delta v)$
for convenience. We have
\begin{eqnarray}
  && \mathcal U F (\alpha, \beta, K, K', \phi) \nonumber \\
  &=&
  -{\alpha K^\alpha \over \xi} p
  \int_{-\infty}^0
      {
       1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
      }
  {1 + b \1{x < -q} \over (K - x)^{\alpha + 1}} dx \nonumber \\
  && -{\beta K'^\beta \over \xi} (1 - p)
  \int_{0}^\infty
  {
   1 \over \left[ (1 - \phi) e^r + \phi e^x \right]^{\xi}
  }
  {1 + b \1{x < -q} \over (K' + x)^{\beta + 1}} dx
  \label{eq:xxie1.0}
\end{eqnarray}

@@

\subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
Figure \ref{fig:Energy_Hill_upper},
\ref{fig:Consumer_Staples_Hill_upper},
and \ref{fig:Information_Technology_lower}
show the Hill estimates of the
lower tail indices of the ``energy'', ``consumer staples'' and ``information
technology'' sectors of the S\&P 500 index, respectively.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Energy_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 32 stocks'
    daily return series in the {\it Energy} sector of Standard \& Poor
    500 index. Each circle coresponds to a Hill estimate; the grey
    triangles above and below it mark the 97.5\% and 2.5\% quantiles
    of its approximate normal distribution.
    The low and high red lines mark the median of the 2.5\% quantiles
    and median of the 97.5\% quantiles, respectively.
    The data are from {\it Yahoo Finance} and the labels on
    the horizontal axis are Yahoo symbols of the stocks. The data span
    from 2010-01-01 to 2015-01-01 and comprise $n=1304$
    observations. $k=(\ln n)^2 = 49$ upper order statistics are used
    for computing $\alpha_n$. 
  }
  \label{fig:Energy_Hill_upper}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Consumer_Staples_Hill_upper.pdf}
  \caption{Hill estimates of the upper tail indices of 30 stocks'
    daily return series in the {\it Consumer Staples} sector of
    Standard \& Poor 500 index.
  }
  \label{fig:Consumer_Staples_Hill_upper}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{Information_Technology_lower.pdf}
  \caption{Hill estimates of the lower-tail indices of 42 stocks' daily
    return series in the {\it Information Technology} sector of S\&P
    500 index.
  }
  \label{fig:Information_Technology_lower}
\end{figure}

\section{Hybrid estimation of the assumed distribution function}
We adopt a hybrid procedure to estimate the parameters of the
distribution function assumed in eq.\eqref{eq:X_distr}: First we
obtain a Hill estimate of the lower- and upper-tail indices of an
equity return and fix $\alpha$ and $\beta$ in \eqref{eq:X_distr}
to their Hill estimates. Then we estimate $K$ and $K'$ by maximizing
the likelihood function with fixed $\alpha$ and $\beta$.

\section{Pickand's Estimator}
Pickands (1975) \cite{pickands1975statistical} proposed a different
approach to estimate the tail index than that of Hill. Assume
$\{x_i\}_{i=1}^n$ are samples from the distribution of $X$ and let $U(t)$
denote the quantile of $1 - 1/t$ of this distribution, i.e.
\[
P(X > U(t)) = {1 \over t}
\]
The key idea of Pickands' estimator is to observe
\[
\lim_{t \to \infty} {
  U(c(t) t) - U(t)
  \over
  U(t) - U(t/c(t))
} = 2^{1/\alpha}
\]
for any function $c(t)$ satisfying $c(t) \to 2$ as $t \to \infty$.
Pickands formulated the estimation problem in terms of the extreme
value index $\xi$, which is the reciprocal of the tail index $\alpha$
when the distribution of $X$ is regularly varying (cf. Embrechtsm,
Kl\"uppelberg and Mikosch \cite{Embrechts1997}).

@@

%% \subsubsection{The Energy and the Consumer Staples sectors of S\&P 500}
%% Figure \ref{fig:Energy_Hill_upper} shows the Hill estimates of the
%% tail indices of 32 stocks in the {\it Energy} sector of S\&P 500
%% index; figure \ref{fig:Consumer_Staples_Hill_upper} shows the same of
%% the {\it Consumer Staples} sector.
%% \begin{figure}[htb!]
%%   \centering
%%   \includegraphics[width=\textwidth]{Energy_Hill_upper.pdf}
%%   \caption{Hill estimates of the upper tail indices of 32 stocks'
%%     daily return series in the {\it Energy} sector of Standard \& Poor
%%     500 index. Each circle coresponds to a Hill estimate; the grey
%%     triangles above and below it mark the 97.5\% and 2.5\% quantiles
%%     of its approximate normal distribution.
%%     The low and high red lines mark the median of the 2.5\% quantiles
%%     and median of the 97.5\% quantiles, respectively.
%%     The data are from {\it Yahoo Finance} and the labels on
%%     the horizontal axis are Yahoo symbols of the stocks. The data span
%%     from 2010-01-01 to 2015-01-01 and comprise $n=1304$
%%     observations. $k=(\ln n)^2 = 49$ upper order statistics are used
%%     for computing $\alpha_n$. 
%%   }
%%   \label{fig:Energy_Hill_upper}
%% \end{figure}

%% \begin{figure}[htb!]
%%   \centering
%%   \includegraphics[width=\textwidth]{Consumer_Staples_Hill_upper.pdf}
%%   \caption{Hill estimates of the upper tail indices of 30 stocks'
%%     daily return series in the {\it Consumer Staples} sector of
%%     Standard \& Poor 500 index.
%%   }
%%   \label{fig:Consumer_Staples_Hill_upper}
%% \end{figure}

%% For our purpose, we have excluded a few stocks, though:
%% \begin{figure}[htb!]
%%   \centering
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{WBA_price.pdf}
%%     \caption{{\it Walgreens Boots Alliance} prices}
%%     \label{fig:EBA_prices}
%%   \end{subfigure}
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{WFM_price.pdf}
%%     \caption{{\it Whole Foods Market} prices}
%%     \label{fig:WFM_prices}
%%   \end{subfigure}
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{EL_price.pdf}
%%     \caption{{\it Estee Lauder Cos.} prices}    
%%     \label{fig:EL_prices}
%%   \end{subfigure}
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{CL_price.pdf}
%%     \caption{{\it Colgate-Palmolive} prices}    
%%     \label{fig:CL_prices}
%%   \end{subfigure}
%%   \caption{Plot of prices of {\it Consumer Staples} stocks
%%     excluded from Hill estimates}
%% \end{figure}

%% \begin{itemize}
%% \item {\it Walgreens Boots Alliance}:

%%   As shown in figure (\ref{fig:EBA_prices}),
%%   this stock was traded only in a small fraction of the bank
%%   days and it is hence no surprise that the price varied
%%   tremendously.
%% \item {\it Whole Foods Market}, {\it Estee Lauder Cos.} and {\it
%%   Colgate-Palmolive}

%%   As seen in figures (\ref{fig:WFM_prices}), (\ref{fig:EL_prices}) and
%%   (\ref{fig:CL_prices}),
%%   the prices of these stocks were reduced by half during the
%%   period under consideration. But the price changes are the
%%   result of emission of new shares rather than random fluctuations.
%% \end{itemize}

%% Figure \ref{fig:Energy_Hill_upper} and
%% \ref{fig:Consumer_Staples_Hill_upper}
%% are suggestive of the conclusion that excluding price
%% movements due to deterministic events, tail indices of stock return
%% series tend to have the same value, within a reasonable confidence
%% interval.

%% If we look instead at the scales, differences among the stock return
%% series are however rather large. Figure (\ref{fig:Energy_Hill_Scales})
%% and (\ref{fig:Consumer_Staples_Hill_Scales}) show the Hill estimates of
%% the scale parameters of the stocks in the S\&P 500 {\it Energy} and
%% {\it Consumer Staples} sectors, respectively.
%% \begin{figure}[htb!]
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{Energy_Hill_scales.pdf}
%%     \caption{{\it Energy} scale estimates}    
%%     \label{fig:Energy_Hill_Scales}
%%   \end{subfigure}
%%   \begin{subfigure}{0.45\textwidth}
%%     \includegraphics[width=\textwidth]{Consumer_Staples_Hill_scales.pdf}
%%     \caption{{\it Consumer Staples} scale estimates}    
%%     \label{fig:Consumer_Staples_Hill_Scales}
%%   \end{subfigure}
%%   \caption{Black boxes are Hill estimates of the scale parameters of
%%     the stock return series, while red circles are the scale estimates
%%     of simulated iid. Student's $t$ series with a degree of freedom
%%     equal to the mean value of the estimated tail indices of the stock
%%     return series. The estimates of the Student's $t$ series are
%%     included for comparison with those of the return series.}
%% \end{figure}
%% Clearly the estimated scale parameters can differ by several orders of
%% magnitude.

%% Using the ``Peaks over Threshold'' method and the mean excess
%% function, we also obtain estimates for the tail index ($\alpha$), the
%% scale parameter ($A$) and the shift parameter ($a$) for stocks in the
%% {\it Energy} and the {\it Consumer Staples} sectors of the S\&P 500
%% index. The results are plotted in figure
%% \ref{fig:Energy_OLS_estimates} and
%% \ref{fig:Consumer_Staples_OLS_estimates},
%% respectively.
%% \begin{figure}[htb!]
%%   \includegraphics[width=\textwidth]{Energy_OLS_estimates.pdf}
%%   \caption{Tail parameter estimates of {\it Energy} stocks. The top
%%     plot shows the tail index estimates, the middle plot shows the
%%     10-based logarithm of the scale estimates and bottom plot shows
%%     the estimates of the shift parameter.
%%   }
%%   \label{fig:Energy_OLS_estimates}
%% \end{figure}

%% \begin{figure}[htb!]
%%   \includegraphics[width=\textwidth]{Consumer_Staples_OLS_estimates.pdf}
%%   \caption{Tail parameter estimates of {\it Consumer Staples}
%%     stocks. The top 
%%     plot shows the tail index estimates, the middle plot shows the
%%     10-based logarithm of the scale estimates and bottom plot shows
%%     the estimates of the shift parameter.
%%   }
%%   \label{fig:Consumer_Staples_OLS_estimates}
%% \end{figure}

@@

%% \subsubsection{The Information Technology sector of S\&P 500}
%% Compared with the sectors of energy and consumer staples, which enjoy
%% a relatively stable demand on their products, companies of information
%% technology are more subject to volatile demand and competition. As a
%% result, one can expect their stock prices to be more volatile, implying
%% lower tail indices and larger differences between the tail indices of
%% different companies. In this section we investigate how these companies
%% differ in terms of their tail indices and scale parameters.

%% Figure \ref{fig:Information_Technology_Hill} shows the Hill
%% estimates of 42 stocks in the {\it Information Technology} sector. Daily
%% closing prices of these stocks have been available since 2000-01-01 and
%% earlier.
%% \begin{figure}[htb!]
%%   \centering
%%   \includegraphics[width=\textwidth]{Information_Technology_Hill.pdf}
%%   \caption{Hill estimates of the tail indices of 42 stocks' daily
%%     return series in the {\it Information Technology} sector of Standard
%%     \& Poor 500 index.
%%   }
%%   \label{fig:Information_Technology_Hill}
%% \end{figure}
%% It is seen in the figure that most of the estimates fall within the
%% interval spanned by the confidence bands. Thus, given the estimation
%% precision, these are consistent with the similarity conclusion of 
%% \S\ref{sec:GDA}.

@@

%% \subsection{Temporal changes of the parameters}

@@

\bibliographystyle{unsrt}
\bibliography{../../thesis/econophysics}
\end{document}
